Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv',sep = '\t')
names(pf)
dim(pf)
p1=qplot(x=age,y=friend_count,data=pf)
#or
p2=qplot(age,friend_count,data =pf)
grid.arrange(p1,p2)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_point(alpha = 1/20)+
  xlim(13,90)

#Alpha is used when you have a huge amount of dots
#in the above example we are saying it will take 20 dots now to show
#what was 1 dot before
summary(pf$age)
```

***
### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_jitter(alpha = 1/20)+
  xlim(13,90)+
  ggtitle('Friend Count by Age')
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_point(alpha = 1/20)+
  xlim(13,90)+
  coord_trans(ytrans='sqrt')+
  ggtitle('Friend Count by Age')
#sqrt function
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_point(alpha = 1/20,position=position_jitter(h=0))+
  xlim(13,90)+
  coord_trans(ytrans='sqrt')+
  ggtitle('Friend Count by Age')
```

#### What do you notice?
#The scales change to put more focus on where the data is heaviest.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_point(alpha = 1/50,position=position_jitter(h=0))+
  xlim(13,90)+
  coord_trans(ytrans='sqrt')+
  ggtitle('Friend Count by Age')

ggsave('NoBreaks.png')
#Tickmarks don't show up
get(w)
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)

age_groups <- group_by(pf,age)
pf.fc_by_age<-summarise(age_groups,
          friend_count_mean=mean(friend_count),
          friend_count_median=median(friend_count),
          n = n())
pf.fc_by_age<- arrange(pf.fc_by_age)
head(pf.fc_by_age)

#OR 

pf.fc_by_age2<-pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)

pf.fc_by_age2
#Common functions
#filter()
#group_by()
#mutate()
#arrange()
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(age,friend_count_mean),data=pf.fc_by_age) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

ggplot(aes(x=age,y=friend_count),data=pf) +
  coord_cartesian(xlim = c(13, 70),ylim=c(0,1000))+
  geom_point(alpha = 1/20,position=position_jitter(h=0),
             color = 'orange')+
  geom_line(stat='summary',fun.y = mean)+
  geom_line(stat='summary',fun.y = quantile,prob=.1,
            linetype =2, color = 'blue')+
  geom_line(stat='summary',fun.y = quantile,prob=.5,
            color = 'blue')+
  geom_line(stat='summary',fun.y = quantile,prob=.9,
            linetype =2, color = 'blue')+
  ggtitle('Friend Count by Age')

  
#Second line gives the 10 percent quantile of plot
#Fourth line give 90 percent quantile(90% of users under)
#To zoom in, the code should use thecoord_cartesian(xlim = c(13, 90)) layer #rather than xlim(13, 90) layer.
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

